---
title: "CUOC Single Transferable Vote Election"
date: "11/16/2021"
author: "Jackie Budka"
output: html_notebook
---

## Help
If a candidate drops out of a race/wins incompatible positions/gets eaten by a brog, go into the excel file and select the column where that person is running for that position. Save and close the excel file and rerun this program.

Load packages
```{r}
library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(janitor)
library(STV)
```

Import data and format
```{r}
raw_ballots <- read_excel("CUOC_Ballot.xlsx") %>%
  clean_names() %>%
  as.data.frame() %>%
  select(-"timestamp")
```

President
```{r}
president_raw <- raw_ballots %>%
  select(starts_with("president_")
  )
president_candidates <- colnames(president_raw)

president_1 <- cleanBallots(president_raw)
validateBallots(president_1)

president_winner <- stv(president_1, seats = 1)
  
```

Vice President
```{r}
raw_vice_president_raw <- raw_ballots %>%
  select(starts_with("vice_president_")
  )
vice_president_candidates <- colnames(raw_vice_president_raw)

vice_president_1 <- cleanBallots(raw_vice_president_raw)
validateBallots(vice_president_1)

vice_president_winner <- stv(vice_president_1, seats = 1)
```

Treasurer
```{r}
treasurer_raw <- raw_ballots %>%
  select(starts_with("treasurer_")
  )
treasurer_candidates <- colnames(treasurer_raw)

treasurer_1 <- cleanBallots(treasurer_raw)
validateBallots(treasurer_1)

treasurer_winner <- stv(treasurer_1, seats = 1)
```

Secretary
```{r}
secretary_raw <- raw_ballots %>%
  select(starts_with("secretary_")
  )
secretary_candidates <- colnames(secretary_raw)

secretary_1 <- cleanBallots(secretary_raw)
validateBallots(secretary_1)

secretary_winner <- stv(secretary_1, seats = 1)
```

Hiking Chair
```{r}
hiking_chair_raw <- raw_ballots %>%
  select(starts_with("hiking_chair_")
  )
hiking_chair_candidates <- colnames(hiking_chair_raw)

hiking_chair_1 <- cleanBallots(hiking_chair_raw)
validateBallots(hiking_chair_1)

hiking_chair_winner <- stv(hiking_chair_1, seats = 3)
```

Climbing Chair
```{r}
climbing_chair_raw <- raw_ballots %>%
  select(starts_with("climbing_chair_")
  )
climbing_chair_candidates <- colnames(climbing_chair_raw)

climbing_chair_1 <- cleanBallots(climbing_chair_raw)
validateBallots(climbing_chair_1)

climbing_chair_winner <- stv(climbing_chair_1, seats = 2)
```

Canoeing Chair
```{r}
canoeing_chair_raw <- raw_ballots %>%
  select(starts_with("canoeing_chair_")
  )
canoeing_chair_candidates <- colnames(canoeing_chair_raw)

canoeing_chair_1 <- cleanBallots(canoeing_chair_raw)
validateBallots(canoeing_chair_1)

canoeing_chair_winner <- stv(canoeing_chair_1, seats = 2)
```

Mountain Biking Chair
```{r}
mountain_biking_chair_raw <- raw_ballots %>%
  select(starts_with("mountain_biking_chair_")
  )
mountain_biking_chair_candidates <- colnames(mountain_biking_chair_raw)

mountain_biking_chair_1 <- cleanBallots(mountain_biking_chair_raw)
validateBallots(mountain_biking_chair_1)

mountain_biking_chair_winner <- stv(mountain_biking_chair_1, seats = 2)
```

Back Country Skiing Chair
```{r}
back_country_skiing_chair_raw <- raw_ballots %>%
  select(starts_with("back_country_skiing_chair_")
  )
back_country_skiing_chair_candidates <- colnames(back_country_skiing_chair_raw)

back_country_skiing_chair_1 <- cleanBallots(back_country_skiing_chair_raw)
validateBallots(back_country_skiing_chair_1)

back_country_skiing_chair_winner <- stv(back_country_skiing_chair_1, seats = 2)
```

Cross Country Skiing Chair
```{r}
cross_country_skiing_chair_raw <- raw_ballots %>%
  select(starts_with("cross_country_skiing_chair_")
  )
cross_country_skiing_chair_candidates <- colnames(cross_country_skiing_chair_raw)

cross_country_skiing_chair_1 <- cleanBallots(cross_country_skiing_chair_raw)
validateBallots(cross_country_skiing_chair_1)

cross_country_skiing_chair_winner <- stv(cross_country_skiing_chair_1, seats = 2)
```

White Water Chair
```{r}
white_water_chair_raw <- raw_ballots %>%
  select(starts_with("white_water_chair_")
  )
white_water_chair_candidates <- colnames(white_water_chair_raw)

white_water_chair_1 <- cleanBallots(white_water_chair_raw)
validateBallots(white_water_chair_1)

white_water_chair_winner <- stv(white_water_chair_1, seats = 2)
```

Caving Chair
```{r}
caving_chair_raw <- raw_ballots %>%
  select(starts_with("caving_chair_")
  )
caving_chair_candidates <- colnames(caving_chair_raw)

caving_chair_1 <- cleanBallots(caving_chair_raw)
validateBallots(caving_chair_1)

caving_chair_winner <- stv(caving_chair_1, seats = 2)
```

Fishing Chair
```{r}
fishing_chair_raw <- raw_ballots %>%
  select(starts_with("fishing_chair_")
  )
fishing_chair_candidates <- colnames(fishing_chair_raw)

fishing_chair_1 <- cleanBallots(fishing_chair_raw)
validateBallots(fishing_chair_1)

fishing_chair_winner <- stv(fishing_chair_1, seats = 2)
```

Slacklining Chair
```{r}
slacklining_chair_raw <- raw_ballots %>%
  select(starts_with("slacklining_chair_")
  )
slacklining_chair_candidates <- colnames(slacklining_chair_raw)

slacklining_chair_1 <- cleanBallots(slacklining_chair_raw)
validateBallots(slacklining_chair_1)

slacklining_chair_winner <- stv(slacklining_chair_1, seats = 2)
```

Media Chair
```{r}
media_chair_raw <- raw_ballots %>%
  select(starts_with("media_chair_")
  )
media_chair_candidates <- colnames(media_chair_raw)

media_chair_1 <- cleanBallots(media_chair_raw)
validateBallots(media_chair_1)

media_chair_winner <- stv(media_chair_1, seats = 2)
```

Service Chair
```{r}
service_chair_raw <- raw_ballots %>%
  select(starts_with("service_chair_")
  )
service_chair_candidates <- colnames(service_chair_raw)

service_chair_1 <- cleanBallots(service_chair_raw)
validateBallots(service_chair_1)

service_chair_winner <- stv(service_chair_1, seats = 1)
```

46 Climbs Chair
```{r}
i46_climbs_chair_raw <- raw_ballots %>%
  select(starts_with("i46_climbs_chair_")
  )
i46_climbs_chair_candidates <- colnames(i46_climbs_chair_raw)

i46_climbs_chair_1 <- cleanBallots(i46_climbs_chair_raw)
validateBallots(i46_climbs_chair_1)

i46_climbs_chair_winner <- stv(i46_climbs_chair_1, seats = 1)
```

Forest Management Chair
```{r}
forest_management_chair_raw <- raw_ballots %>%
  select(starts_with("forest_management_chair_")
  )
forest_management_chair_candidates <- colnames(forest_management_chair_raw)

forest_management_chair_1 <- cleanBallots(forest_management_chair_raw)
validateBallots(forest_management_chair_1)

forest_management_chair_winner <- stv(forest_management_chair_1, seats = 1)
```
